### 2009-11-05 doc/manuals/user_interface/ui-job.tex
bring up to date arc data client examples
Finished job commands

Since  the  information  about  a job retrieved from a cluster can be slightly out of date if the user very recently
submitted or removed a job, a warning is issued when this command is run. The \verb#--force# option disables this warning.

If the job list is not empty when invoking syncronisation, the old jobs will be merged with the new jobs, unless the \verb#--truncate# option is given, in which case the job list will first be truncated and then the new jobs will be added.

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsub [options] [filename]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{url}&explicitly select or reject (-) a specific site\\
   \texttt{-i, --index}&\textit{url}&explicitly select or reject (-) a specific index server\\
   \texttt{-e, --jobdescrstring}&\textit{filename}&string describing the job to be submitted\\
   \texttt{-f, --jobdescrfile}&\textit{filename}&file describing the job to be submitted\\
   \texttt{-j, --joblist}&\textit{filename}&file where user's job information will be stored\\
%   \texttt{-D, --dryrun}&&add dryrun option to the job description\\
   \texttt{-x, --dumpdescription}&&do not submit -- dump transformed job description to stdout\\
%   \texttt{-U, --unknownattr}&&allow unknown attributes in the job description\\
   \texttt{-t, --timeout}&\textit{seconds}&timeout in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-b, --broker}&\textit{string}&select broker method (default is Random)\\
   \texttt{-n, --dolocalsandbox}& &store job descriptions in local sandbox (useful for eventual resubmission/migration)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
   Arguments:&&\\
   \texttt{filename}&&file describing the job(s) to be submitted\\
\end{longtable}

@@

\verb# ARC0:ldap://ce.ng.eu:2135/nordugrid-cluster-name=ce.ng.eu,Mds-Vo-name=local,o=grid#
\end{framed}

@@

A simple \textit{"Hello World"} job could look like:

\begin{shaded}
 arcsub -c ARC0:ldap://grid.ng.org:2135/nordugrid-cluster-name=grid.ng.org,Mds-Vo-name=local,o=grid -f job.jsdl
\end{shaded}

A user has to have valid credentials (see Section~\ref{sec:proxy}) and be authorised at the specified site. The test file \texttt{job.jsdl} is shown below.

@@

The \verb#-c# option can be used to \textbf{force} a job to be
submitted to a particular site (cluster), or to reject submission to a
site. The matching is done by string match to the site name (i.e.
hostname) as defined in the Information System, or to an alias, as
defined in user configuration file (see
Section~\ref{sec:client.conf}).  The \verb#-c# option can be repeated
several times, for example:
\begin{verbatim}
    arcsub -c alias1 -c alias2 myjob.xrsl
\end{verbatim}
This will submit a job to either \verb#alias1# or
\verb#alias2#. To submit a job to any site except
\verb#badsite#, use \verb#-# sign in front of the name:
\begin{verbatim}
    arcsub -c -badsite myjob.xrsl
\end{verbatim}

@@

will print out the steps taken by the ARC client to find the
best cluster satisfying your job requirements. A default value for
the debug level can be set in the user's configuration file.

It often happens that some sites that \verb#arcsub# has to contact
are slow to answer, or are down altogether. This will not prevent
you from submitting a job, but will slow down the submission. To
speed it up, you may want to specify a shorter timeout (default is
20 seconds) with the \verb#-t# option:
\begin{verbatim}
    arcsub -t 5 myjob.xrsl
\end{verbatim}

A default value for the timeout can be set in the user's configuration file.

\input{ui-brokers}

@@

\begin{shaded}
   \uicommand{arcstat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename}& file containing a list of jobIDs\\
   \texttt{-c, --cluster}& & show information about a site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-i, --indexurl}& \textit{url} &URL of an index service\\
   \texttt{-q, --queues}&&show information about clusters and queues\\
   \texttt{-l, --long}& & long format (extended information)\\
   \texttt{-t, --timeout}& \textit{time}& timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

The arcstat command returns the status of jobs submitted to the Grid. Then \texttt{-c} and \texttt{-i} accept arguments in the GRID:URL notation explained in the description of \texttt{arcsub}.

Different sites may report slightly different job states, depending on
the installed software version.% A summary of essential job
%states\index{job:states} is:

%  ---  Does the table below need updating? ---

% \begin{longtable}{l|l|p{8cm}}
% ARC 0.3, ARC 0.4 & ARC 0.5, ARC0.6 & Description\\ \hline
%                    &\texttt{ACCEPTING} &job has reached the site\\
% \texttt{ACCEPTED}  &\texttt{ACCEPTED}  &job submitted but not yet processed\\
% \texttt{PREPARING} &\texttt{PREPARING} &input files are being retreived\\
%                    &\texttt{PREPARED}  &input files are retreived\\
% \texttt{SUBMITTING}&\texttt{SUBMITTING}&interaction with LRMS ongoing\\
% \texttt{INLRMS: Q} &\texttt{INLRMS:Q}  &job is queued by LRMS\\
% \texttt{INLRMS: R} &\texttt{INLRMS:R}  &job is running\\
%                    &\texttt{INLRMS:S}  &job is suspended\\
%                    &\texttt{INLRMS:E}  &job is finishing in LRMS\\
%                    &\texttt{INLRMS:O}  &job is in any other LRMS state\\
% \texttt{CANCELING} &\texttt{KILLING}   &job is being cancelled by user request\\
%                    &\texttt{EXECUTED}  &job is completed in LRMS\\
% \texttt{FINISHING} &\texttt{FINISHING} &output files are being transferred\\
% \texttt{FINISHED}  &\texttt{FINISHED}  &job is finished\\
%                    &\texttt{FAILED}    &job is finished with an error\\
%                    &\texttt{KILLED}    &job is cancelled by user request\\
% \texttt{DELETED}   &\texttt{DELETED}   &job is removed due to expiration time\\
% \end{longtable}

@@

It is often useful to monitor the job progress by checking what it
prints on the standard output or error. The command \texttt{arccat}
\index{arccat}\index{commands:arccat} assists here, extracting the
corresponding information from the execution cluster and pasting it
on the user's screen. It works both for running tasks and for the
finished ones. This allows a user to check the output of the
finished task without actually retreiving it.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename} & file containing a list of job IDs\\
   \texttt{-c, --cluster}& & show information about clusters\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-o, --stdout}& & show the stdout of the job (default)\\
   \texttt{-e, --stderr}& & show the stderr of the job\\
   \texttt{-l, --gmlog}& & show the grid manager's error log of the job\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

The \texttt{arccat} command can return the standard output of a job
(\texttt{-o} option), the standard error (\texttt{-e} option) and the
errors reported by the Grid Manager (\texttt{-l} option).

\begin{framed}

\end{framed}

@@

To retrieve the results of a finished job, the \texttt{arcget}
\index{arcget}\index{commands:arcget} command should be used. It
will download the files specified by the \texttt{outputfiles}
attribute of job description to the user's computer.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcget [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-D, --dir} & \textit{dirname} & download directory (the job directory will be created in this directory)\\
   \texttt{-k, --keep}& & keep files on gatekeeper (do not clean)\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

Only the results of jobs that have finished can be downloaded. The job
can be referred to either by the \texttt{jobID} that was returned by
\texttt{arcsub} at submission time, or by its name, if the job
description contained a job name attribute.

@@

It happens that a user may wish to cancel a job. This is done by using
the \texttt{arckill} \index{arckill}\index{commands:arckill} command. A
job can be killed amost on any stage of processing through the Grid.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arckill [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}& & show information about clusters\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-k, --keep}& & keep files on gatekeeper (do not clean)\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

% \subsection{arcresub}
% \label{sec:arcresub}
% 
% Quite often it happens that a user would like to re-submit a job, but
% has difficulties recovering the original job description xRSL file.
% This happens when xRSL files are created by scripts on-fly, and
% matching of xRSL to the job ID is not straightforward. The utility
% called \texttt{arcresub}\index{arcresub}\index{commands:arcresub} helps
% in such situations, allowing users to resubmit jobs known only by
% their job IDs.
% 
% \begin{framed}
%    Only jobs where the \verb#gmlog#\index{gmlog} attribute was
%    specified in the job description can be resubmitted.
% \end{framed}
% 
% \hspace*{0.5cm}
% \begin{shaded}
%    \uicommand{arcresub [options] [job ...]}
% \end{shaded}
% \versions{ARC 0.9}
% \begin{longtable}{llp{8cm}}
%    Options:&&\\
%    \texttt{-a, -all}& & all jobs\\
%    \texttt{-i, -joblist}& \textit{filename} & file containing a list of jobIDs\\
%    \texttt{-c, -cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
%    \texttt{-C, -clustlist}&\verb#[-]#textem{filename}&list of sites (clusters) to select or reject\\
%    \texttt{-s, -status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
%    \texttt{-k, -kluster}&\verb#[-]#textem{name}&explicitly select or
%    reject a specific site (cluster) as re-submission target\\
%    \texttt{-K, -Klustlist}&\verb#[-]#textem{filename}&list of
%    clusters to select or reject as re-submission target\\
%    \texttt{-g, -giisurl}& \textit{url} &URL of a central Information System server\\
%    \texttt{-G, -giislist}&\textit{filename}&list of GIIS URLs\\
%    \texttt{-o, -joblist}&\textit{filename}&file where the job IDs will be stored\\
%    \texttt{~~~~-dryrun}&&add dryrun option to the xRSL\\
%    \texttt{~~~~-dumpxrsl}&&do not submit -- dump transformed xRSL to stdout\\
%    \texttt{~~~~-keep}& & keep files on gatekeeper (do not clean)\\
%    \texttt{-t, -timeout}& \textit{time} & timeout for queries (default 40 sec)\\
%    \texttt{-d, -debug}& \textit{debuglevel} &debug level, from -3 (quiet) to 3 (verbose) - default 0\\
%    \texttt{-x, -anonymous}& & use anonymous bind for queries (default)\\
%    \texttt{-X, -gsi}& & use GSI-GSSAPI bind for queries\\
%    \texttt{-v, -version}& & print version information\\
%    \texttt{-h, -help}& & print help page\\
%    Arguments:&&\\
%    \texttt{job ...} && list of job IDs and/or jobnames\\
% \end{longtable}

@@

If a job fails, or you are not willing to retrieve the results for
some reasons, a good practice for users is not to wait for the Grid
Manager to clean up the job leftovers, but to use \texttt{arcclean}
\index{arcclean}\index{commands:arcclean} to release the disk space
and to remove the job ID from the list of submitted jobs and from
the Information System.

@@

Only jobs that have finished can be cleaned.

% \subsection{arcrenew}
% \label{sec:arcrenew}
% 
% Quite often, the user proxy expires while the job is still running (or
% waiting in a queue). In case such job has to upload output files to a
% Grid location (Storage Element), it will fail. By using the \texttt{arcrenew}
% \index{arcrenew}\index{commands:arcrenew} command, users can upload
% a new proxy to the job. This can be done while a job is still running,
% thus preventing it from failing, or whithin 24 hours (or whatever is
% the expiration time set by the site) after the job
% end. In the latter case, the Grid Manager will attempt to finalize
% the job by uploading the output files to the desired location.
% 
% \hspace*{0.5cm}
% \begin{shaded}
%    \uicommand{arcrenew [options] [job ...]}
% \end{shaded}
% \versions{ARC 0.9}
% \begin{longtable}{llp{8cm}}
%    Options:&&\\
%    \texttt{-a, -all}& & all jobs\\
%    \texttt{-i, -joblist}& \textit{filename} & file containing a list of jobIDs\\
%    \texttt{-c, -cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
%    \texttt{-C, -clustlist}&\verb#[-]#textem{filename}&list of sites (clusters) to select or reject\\
%    \texttt{-s, -status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
%    \texttt{-t, -timeout}& \textit{time} & timeout for queries (default 40 sec)\\
%    \texttt{-d, -debug}& \textit{debuglevel} &debug level, from -3 (quiet) to 3 (verbose) - default 0\\
%    \texttt{-x, -anonymous}& & use anonymous bind for queries (default)\\
%    \texttt{-X, -gsi}& & use GSI-GSSAPI bind for queries\\
%    \texttt{-v, -version}& & print version information\\
%    \texttt{-h, -help}& & print help page\\
%    Arguments:&&\\
%    \texttt{job ...} && list of job IDs and/or jobnames\\
% \end{longtable}
% 
% Prior to using \texttt{arcrenew}, be sure to actually create the
% new proxy!
%

% \subsection{Auxilliary files}\label{sec:joblists}
% 
% User Interface keeps local job lists in two files:
% {\$}\verb#HOME/.ngjobs# and {\$}\verb#HOME/.arc/history#\footnote{In
%   ARC $\leq$ 0.5.48, {\$}\texttt{HOME/.nghistory}}.
% 
% \textbf{{\$}\texttt{HOME/.ngjobs}} is a local list of the user's active
% jobs. When a job is successfully submitted, it is added to this list,
% and when it is removed from the remote site, it is removed from this
% list. This list is used as the list of all active jobs when the user
% specifies \verb#-a# option to the various ARC user interface commands.
% For information about how to reconstruct this file in case it is
% damaged or you relocate to a different workstation, see
% section~\ref{sec:arcsync} about the \texttt{arcsync} command.
% 
% \textbf{{\$}\texttt{HOME/.arc/history}} contains the \texttt{jobID}s of
% the jobs the user has submitted together with the time of
% submission. This file is purely informational.

>>>>

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsub [options] [filename]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{url}&explicitly select or reject (-) a specific site\\
   \texttt{-i, --index}&\textit{url}&explicitly select or reject (-) a specific index server\\
   \texttt{-e, --jobdescrstring}&\textit{filename}&string describing the job to be submitted\\
   \texttt{-f, --jobdescrfile}&\textit{filename}&file describing the job to be submitted\\
   \texttt{-j, --joblist}&\textit{filename}&file where user's job information will be stored\\
%   \texttt{-D, --dryrun}&&add dryrun option to the job description\\
   \texttt{-x, --dumpdescription}&&do not submit -- dump transformed job description to stdout\\
%   \texttt{-U, --unknownattr}&&allow unknown attributes in the job description\\
   \texttt{-b, --broker}&\textit{string}&select broker method (default is Random)\\
   \texttt{-n, --dolocalsandbox}& &store job descriptions in local sandbox (useful for eventual resubmission/migration)\\
   \texttt{-t, --timeout}&\textit{seconds}&timeout in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
   Arguments:&&\\
   \texttt{filename}&&file describing the job(s) to be submitted\\
\end{longtable}

@@

\verb# ARC0:ldap://ce.ng.eu:2135/nordugrid-cluster-name=ce.ng.eu,Mds-Vo-name=local,o=grid#

It is strongly recommended to use aliases for these long URLs. Aliases are specified in the configuration file (see Section~\ref{sec:client.conf}).
\end{framed}

@@

A simple \textit{"Hello World"} job can look like:

\begin{shaded}
 arcsub -c my-test-site job.jsdl
\end{shaded}

The \verb#-c# option can be repeated several times, for example:
\begin{verbatim}
    arcsub -c alias1 -c alias2 job.xrsl
\end{verbatim}
This will submit a job to either \verb#alias1# or \verb#alias2#. To submit a job to any site except
\verb#badsite#, use \verb#-# sign in front of the name:
\begin{verbatim}
    arcsub -c -badsite job.xrsl
\end{verbatim}

A user has to have valid credentials (see Section~\ref{sec:proxy}) and be authorised at the specified site. A test file \texttt{job.jsdl} is shown below.

@@

In order to keep track of submitted jobs, ARC client stores information in a
dedicated file, by default located in \texttt{{\$}HOME/.arc/jobs.xml}. It is
sometimes convenient to keep separate lists (e.g., for different kinds of jobs),
to be used later with e.g. \verb#arcstat#. This is achieved with the help of
\verb#-j# command line option.

% Description of brokers in a separate file
\input{ui-brokers}

If you plan to resubmit or migrate jobs, you will have to use command line
option \verb#-n#, which will instruct the client to store complete job descriptions
in a local sandbox, such that a resubmitted/migrated job will be identical to the
original one.

It often happens that some sites that \verb#arcsub# has to contact
are slow to answer, or are down altogether. This will not prevent
you from submitting a job, but will slow down the submission. To
speed it up, you may want to specify a shorter timeout (default is
20 seconds) with the \verb#-t# option:
\begin{verbatim}
    arcsub -t 5 myjob.jsdl
\end{verbatim}

Default value for the timeout can be set in the user's configuration file.

@@

will print out the steps taken by the ARC client to find the
best cluster satisfying your job requirements. Possible diagnostics degrees, in the
order of increasing verbosity, are: \texttt{FATAL}, \texttt{ERROR}, \texttt{WARNING},
\texttt{INFO}, \texttt{DEBUG} and \texttt{VERBOSE}. Default is \texttt{WARNING}, and
it can be set to another value in the user's configuration file.

Default configuration file is {\$}HOME/.arc/client.conf. However, a user can chose any
other pre-defined configuration through option \verb#-z#.

Command line option \verb#-v# prints out version of the installed ARC client, and option
\verb#-h# provides a short help text.

@@

\begin{shaded}
   \uicommand{arcstat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename}& file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{name}&explicitly select or reject a specific site\\
%   \texttt{-c, --cluster}& & show information about a site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
%   \texttt{-i, --index}& \textit{url} &URL of an index service\\
   \texttt{-l, --long}& & long format (extended information)\\
   \texttt{-t, --timeout}& \textit{time}& timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

The arcstat command returns the status of jobs in the Grid, and is typically issued with a
job ID (as returned by \verb#arcsub#) as an argument. It is also possible to use job name instead of
ID, but if several jobs have identical names, information will be collected about all of them. 
More than one job ID and/or name can be given.

If the \verb#-l# option is given, extended information is printed.

Options \verb#-a#, \verb#-c#, \verb#-s# and \verb#-j# do not use job ID or names. By
specifying the \verb#-a# option, the status of all active jobs will be shown. If the \verb#-j# option
is used, the list of jobs is read from a file with the specified filename, instead of
the default one (\texttt{{\$}HOME/.arc/jobs.xml}).

Option \verb#-c# accepts arguments in the \texttt{GRID:URL} notation,
as explained in the description of \texttt{arcsub}, or their aliases as 
specified in the configuration file.

Different sites may report different job states, depending on
the installed grid middleware version. Typical values can be e.g. 
``Accepted'', ``Preparing'', ``Running'', ``Finished'' or ``Deleted''.
Please refer to the respective middleware documentation for job state model
description.

Command line option \verb#-s# will instruct the client to display information
of only those jobs which status matches the instruction. This option must be given
together with either \verb#-a# or \verb#-c# ones, e.g.:
\begin{verbatim}
    arcstat -as Finished
\end{verbatim}

Other command line options are identical to those of \verb#arcsub#.

@@

It is often useful to monitor the job progress by checking what it
prints on the standard output or error. The command \texttt{arccat}
\index{arccat}\index{commands:arccat} assists here, extracting the
corresponding information from the execution cluster and dumping it
on the user's screen. It works both for running tasks and for the
finished ones. This allows a user to check the output of the
finished task without actually retreiving it.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of job IDs\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{url}&explicitly select or reject (-) a specific site\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-o, --stdout}& & show the stdout of the job (default)\\
   \texttt{-e, --stderr}& & show the stderr of the job\\
   \texttt{-l, --gmlog}& & show the grid manager's error log of the job\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

The \texttt{arccat} command returns the standard output of a job
(\texttt{-o} option), the standard error (\texttt{-e} option) or
errors reported by either Grid Manager or A-REX (\texttt{-l} option).

Other command line options have the same meaning as in \verb#arcstat#.

@@

To retrieve the results of a finished job, the \texttt{arcget}
\index{arcget}\index{commands:arcget} command should be used. It
will transfer the files specified for download in job description
to the user's computer.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcget [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-D, --dir} & \textit{dirname} & download path (the job directory will be created in that location)\\
   \texttt{-k, --keep}& & keep files in the Grid (do not clean)\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

Only the results of jobs that have finished can be downloaded. Just like in \verb#arstat# 
and \verb#arccat# cases, the job can be referred to either by the \texttt{jobID} that was returned by
\texttt{arcsub} at submission time, or by its name, if the job
description contained a job name attribute.

By default, the job is downloaded into a newly created directory in the current path, with the
name typically being a large random number. In order to instruct \verb#arcget# to use another
path, use option \verb#-D# (note the capital ``D''), e.g.
\begin{verbatim}
    arcget -D /tmp/myjobs "Test job nr 1"
\end{verbatim}

\begin{framed}
 After downloading, your jobs will be erased from the execution site! Use command line option \verb#-k#
 to keep finished jobs in the Grid.
\end{framed}

Other command line options are identical to those of e.g. \verb#arcstat#.

Since  the  information  about  a job retrieved from a cluster can be slightly out of date if the user very recently
submitted or removed a job, a warning is issued when this command is run. The \verb#-f# option disables this warning.

If the job list is not empty when invoking syncronisation, the old jobs will be merged with the new jobs, unless
the \verb#-T# option is given (note the capital ``T''), in which case the job list will first be truncated and then the new jobs will be added.

@@

It happens that a user may wish to cancel a job. This is done by using
the \texttt{arckill} \index{arckill}\index{commands:arckill} command. A
job can be killed almost at any stage of processing through the Grid.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arckill [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{url}&explicitly select or reject (-) a specific site\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-k, --keep}& & keep files in the Grid (do not clean)\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

If a job is killed, its traces are being cleaned from the Grid. If you wish to keep the killed job
in the system, e.g. for a post-mortem analysis, use the \verb#-k# option.

@@

Command line options have the same meaning as the corresponding ones of \verb#arcstat# and others.

@@

If a job fails or gets killed with \verb#-k# option, or when you are not willing 
to retrieve the results for some reasons, a good practice for users is not to wait 
for the system to clean up the job leftovers, but to use 
\texttt{arcclean}\index{arcclean}\index{commands:arcclean} to release the disk 
space and to remove the job ID from the list of submitted jobs and from the Information System.

@@

Only jobs that have finished or were cancelled can be cleaned.

It happens ever so often that the job is cleaned by the system, or is otherwise unreachable, and yet your 
local job list file still has it listed. Use \verb#-f# option in this case to forcefully remove such stale job
information from the local list.

Other command line options have the same meaning as the corresponding ones of \verb#arcstat# and others.

\subsection{arcrenew}
\label{sec:arcrenew}

Quite often, the user proxy expires while the job is still running (or
waiting in a queue). In case such job has to upload output files to a
Grid location (Storage Element), it will fail. By using the \texttt{arcrenew}
\index{arcrenew}\index{commands:arcrenew} command, users can upload
a new proxy to the job. This can be done while a job is still running,
thus preventing it from failing

If a job has failed in file upload due to expired proxy, \texttt{arcrenew}
can be issued whithin 24 hours (or whatever is
the expiration time set by the site) after the job
end, which must be followed by \texttt{arcresume}. The Grid
Manager or A-REX will then attempt to finalize
the job by uploading the output files to the desired location.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcrenew [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

\begin{framed}
 Prior to using \texttt{arcrenew}, be sure to actually create the
new proxy by running \verb#arcproxy#!
\end{framed}

Command line options have the same meaning as the corresponding ones of \verb#arcstat# and others.

\subsection{arcresume}
\label{sec:arcresume}

In some cases a user may want to restart a failed job, for example, when input
files become available, or the storage element for the output files came back
online, or when a proxy is renewed with \texttt{arcrenew}. This can be done using
the \texttt{arcresume}\index{arcresume}\index{commands:arcresume} command.

\begin{framed}
Make sure your proxy is still valid, or when uncertain, run \verb#arcproxy# followed by 
\verb#arcrenew# before \verb#arcresume#. The job will be resumed from the state where it has failed.
\end{framed}

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcresume [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

Command line options have the same meaning as the corresponding ones of \verb#arcstat# and others.

\subsection{arcresub}
\label{sec:arcresub}
